A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
multiple word section fixes

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis, e.g. `өнүктүрөбүзбү ?' {\em TRANSLATION ?} is analysed as 
өнүк{\tt {\small <v><tv><caus><aor><p1><pl>+}}бы{\tt {\small <qst>}} two words: `өнүк' (verb, transitive, causative, aorist, first person, plural) and `бы' (question clitic).

>>>>

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis.  For example, `өнүктүрөбүзбү ?' \eng{will we develop it?} is analysed as 
өнүк{\tt {\small <v><tv><caus><aor><p1><pl>+}}бы{\tt {\small <qst>}}, which is two words: `өнүк' (verb, transitive, causative, aorist, first person, plural) and `бы' (question clitic).  Likewise, `келатсаң' \eng{if you come} кел{\tt {\small <v><iv><prt\_impf>}}+жат\texttt{{\small <vaux><gna\_cnd><p2><sg>}} is analysed as two words: `кел' (verb, intransitive, imperfect participle), and жат (auxiliary, conditional verbal adverb, second person, singular).
